---
title: "Proj"
author: "Omar Badran - puf311"
date: "2026-07-09"
output: html_document
---


```{r}
library(readxl)
library(writexl)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(irr)
library(corrplot)

library(GGally)

library(purrr)
```

```{r}
df_general <- read_excel("GeneralQuestions.xlsx", sheet="Data")
df_specific <- read_excel("SpecificQuestions.xlsx", sheet="Data")
df_general_annotated <- read_excel("sample_response_general_completed.xlsx", sheet="Sheet1")
df_specific_annotated <- read_excel("sample_response_specific.xlsx", sheet="Sheet1")
```

# 1. Frequency Distributions and tables

```{r}
as.data.frame(str(df_general))
as.data.frame(summary(df_general))
as.data.frame(table(df_general$Category))
as.data.frame(table(df_general$Scenario))

df_counts <- as.data.frame(table(df_general$Category))
colnames(df_counts) <- c("Category", "Frequency")

ggplot(df_counts, aes(x = Category, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3) +
  labs(title = "Category distribution",
       x = "Category",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))

df_counts <- as.data.frame(table(df_general$Scenario))
colnames(df_counts) <- c("Scenario", "Frequency")

ggplot(df_counts, aes(x = Scenario, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3.5) +
  labs(title = "Scenario distribution",
       x = "Scenario",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))

```

```{r}
as.data.frame(str(df_specific))
as.data.frame(summary(df_specific))
as.data.frame(table(df_specific$Company))

df_counts <- as.data.frame(table(df_specific$Company))
colnames(df_counts) <- c("Company", "Frequency")

ggplot(df_counts, aes(x = Company, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3) +
  labs(title = "Company distribution",
       x = "Company",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))


```

```{r}
as.data.frame(str(df_general_annotated))
as.data.frame(summary(df_general_annotated))
as.data.frame(table(df_general_annotated$Model))
as.data.frame(table(df_general_annotated$Category))
as.data.frame(table(df_general_annotated$Scenario))
df_general_annotated |>
  count(Model, Category) |>
  tidyr::pivot_wider(
    names_from = Category,
    values_from = n,
    values_fill = 0
  )


df_counts <- as.data.frame(table(df_general_annotated$Category))
colnames(df_counts) <- c("Category", "Frequency")

ggplot(df_counts, aes(x = Category, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3) +
  labs(title = "Category distribution",
       x = "Category",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))

df_counts <- as.data.frame(table(df_general_annotated$Scenario))
colnames(df_counts) <- c("Scenario", "Frequency")

ggplot(df_counts, aes(x = Scenario, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3.5) +
  labs(title = "Scenario distribution",
       x = "Scenario",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))

df_counts <- as.data.frame(table(df_general_annotated$Model))
colnames(df_counts) <- c("Model", "Frequency")

ggplot(df_counts, aes(x = Model, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3) +
  labs(title = "Model distribution",
       x = "Model",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))
```

```{r}
as.data.frame(str(df_specific_annotated))
as.data.frame(summary(df_specific_annotated))
as.data.frame(table(df_specific_annotated$Model))
as.data.frame(table(df_specific_annotated$Company))
df_specific_annotated |>
  count(Model, Company) |>
  tidyr::pivot_wider(
    names_from = Company,
    values_from = n,
    values_fill = 0
  )

df_counts <- as.data.frame(table(df_specific_annotated$Company))
colnames(df_counts) <- c("Company", "Frequency")

ggplot(df_counts, aes(x = Company, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3) +
  labs(title = "Company distribution",
       x = "Company",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))

df_counts <- as.data.frame(table(df_specific_annotated$Model))
colnames(df_counts) <- c("Model", "Frequency")

ggplot(df_counts, aes(x = Model, y = Frequency)) +
  geom_col(fill = "grey") +
  geom_text(aes(label = Frequency), vjust = -0.5, size = 3) +
  labs(title = "Model distribution",
       x = "Model",
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.title = element_text(size = 12))
```

```{r}
missing_pct <- as.data.frame(round(colSums(is.na(df_general)) / nrow(df_general) * 100, 2))
colnames(missing_pct) <- "Missing (%)"
missing_pct

missing_pct <- as.data.frame(round(colSums(is.na(df_specific)) / nrow(df_specific) * 100, 2))
colnames(missing_pct) <- "Missing (%)"
missing_pct

missing_pct <- as.data.frame(round(colSums(is.na(df_general_annotated)) / nrow(df_general_annotated) * 100, 2))
colnames(missing_pct) <- "Missing (%)"
missing_pct

missing_pct <- as.data.frame(round(colSums(is.na(df_specific_annotated)) / nrow(df_specific_annotated) * 100, 2))
colnames(missing_pct) <- "Missing (%)"
missing_pct
```

# 2. (Weighted) Cohen's Kappa values
## Specific
```{r}
df_accuracy   <- data.frame(df_specific_annotated$accuracy, df_specific_annotated$human_accuracy)
df_safety   <- data.frame(df_specific_annotated$safety, df_specific_annotated$human_safety)
df_completeness <- data.frame(df_specific_annotated$completeness, df_specific_annotated$human_completeness)
df_pr    <- data.frame(df_specific_annotated$professional_referral, df_specific_annotated$human_professional_referral)
df_overall  <- data.frame(df_specific_annotated$overall_quality, df_specific_annotated$human_overall_quality)

# 2. Extract the Kappa values directly using $value
kappa_table <- data.frame(
  Metric = c("Accuracy", "Safety", "Completeness", "Professional Referral", "Overall Quality"),
  Kappa  = c(
    round(kappa2(df_accuracy, weight = "equal")$value,2),
    round(kappa2(df_safety, weight = "equal")$value,2),
    round(kappa2(df_completeness, weight = "equal")$value,2),
    round(kappa2(df_pr, weight = "equal")$value,2),
    round(kappa2(df_overall, weight = "equal")$value,2)
  )
)

kappa_table
```

## General
```{r}
df_accuracy   <- data.frame(df_general_annotated$accuracy, df_general_annotated$human_accuracy)
df_safety   <- data.frame(df_general_annotated$safety, df_general_annotated$human_safety)
df_completeness <- data.frame(df_general_annotated$completeness, df_general_annotated$human_completeness)
df_pr    <- data.frame(df_general_annotated$professional_referral, df_general_annotated$human_professional_referral)
df_overall  <- data.frame(df_general_annotated$overall_quality, df_general_annotated$human_overall_quality)

# 2. Extract the Kappa values directly using $value
kappa_table <- data.frame(
  Metric = c("Accuracy", "Safety", "Completeness", "Professional Referral", "Overall Quality"),
  Kappa  = c(
    round(kappa2(df_accuracy, weight = "equal")$value,2),
    round(kappa2(df_safety, weight = "equal")$value,2),
    round(kappa2(df_completeness, weight = "equal")$value,2),
    round(kappa2(df_pr, weight = "equal")$value,2),
    round(kappa2(df_overall, weight = "equal")$value,2)
  )
)

kappa_table
```
# 3. Average score
## By model
```{r}
#General (AI)

df_general_annotated |> group_by(Model) |> summarize("Avg. Accuracy" = round(mean(accuracy),2),
                                                        "Avg. Safety" = round(mean(safety),2),
                                                        "Avg. Completeness" = round(mean(completeness),2),
                                                        "Avg. PR" = round(mean(professional_referral),2),
                                                        "Overall Average"= round(mean(overall_quality),2))
#General (Human)

df_general_annotated |> group_by(Model) |> summarize("Avg. Accuracy (H)" = round(mean(human_accuracy),2),
                                                        "Avg. Safety (H)" = round(mean(human_safety),2),
                                                        "Avg. Completeness (H)" = round(mean(human_completeness),2),
                                                        "Avg. PR (H)" = round(mean(human_professional_referral),2),
                                                        "Overall Average (H)"= round(mean(human_overall_quality),2))
```

```{r}
#Specific
#Specific (AI)

df_specific_annotated |> group_by(Model) |> summarize("Avg. Accuracy" = round(mean(accuracy),2),
                                                        "Avg. Safety" = round(mean(safety),2),
                                                        "Avg. Completeness" = round(mean(completeness),2),
                                                        "Avg. PR" = round(mean(professional_referral),2),
                                                        "Overall Average"= round(mean(overall_quality),2))
#Specific (Human)

df_specific_annotated |> group_by(Model) |> summarize("Avg. Accuracy (H)" = round(mean(human_accuracy),2),
                                                        "Avg. Safety (H)" = round(mean(human_safety),2),
                                                        "Avg. Completeness (H)" = round(mean(human_completeness),2),
                                                        "Avg. PR (H)" = round(mean(human_professional_referral),2),
                                                        "Overall Average (H)"= round(mean(human_overall_quality),2))
```

## By Category (General Only)
```{r}
#General (AI)

df_general_annotated |> group_by(Category) |> summarize("Avg. Accuracy" = round(mean(accuracy),2),
                                                        "Avg. Safety" = round(mean(safety),2),
                                                        "Avg. Completeness" = round(mean(completeness),2),
                                                        "Avg. PR" = round(mean(professional_referral),2),
                                                        "Overall Average"= round(mean(overall_quality),2))
#General (Human)

df_general_annotated |> group_by(Category) |> summarize("Avg. Accuracy (H)" = round(mean(human_accuracy),2),
                                                        "Avg. Safety (H)" = round(mean(human_safety),2),
                                                        "Avg. Completeness (H)" = round(mean(human_completeness),2),
                                                        "Avg. PR (H)" = round(mean(human_professional_referral),2),
                                                        "Overall Average (H)"= round(mean(human_overall_quality),2))
```
## By Scenario (General Only)
```{r}
#General (AI)

df_general_annotated |> group_by(Scenario) |> summarize("Avg. Accuracy" = round(mean(accuracy),2),
                                                        "Avg. Safety" = round(mean(safety),2),
                                                        "Avg. Completeness" = round(mean(completeness),2),
                                                        "Avg. PR" = round(mean(professional_referral),2),
                                                        "Overall Average"= round(mean(overall_quality),2))
#General (Human)

df_general_annotated |> group_by(Scenario) |> summarize("Avg. Accuracy (H)" = round(mean(human_accuracy),2),
                                                        "Avg. Safety (H)" = round(mean(human_safety),2),
                                                        "Avg. Completeness (H)" = round(mean(human_completeness),2),
                                                        "Avg. PR (H)" = round(mean(human_professional_referral),2),
                                                        "Overall Average (H)"= round(mean(human_overall_quality),2))
```

## By Company (Specific Only)
```{r}
#Specific (AI)

df_specific_annotated |> group_by(Company) |> summarize("Avg. Accuracy" = round(mean(accuracy),2),
                                                        "Avg. Safety" = round(mean(safety),2),
                                                        "Avg. Completeness" = round(mean(completeness),2),
                                                        "Avg. PR" = round(mean(professional_referral),2),
                                                        "Overall Average"= round(mean(overall_quality),2))
#Specific (Human)

df_specific_annotated |> group_by(Company) |> summarize("Avg. Accuracy (H)" = round(mean(human_accuracy),2),
                                                        "Avg. Safety (H)" = round(mean(human_safety),2),
                                                        "Avg. Completeness (H)" = round(mean(human_completeness),2),
                                                        "Avg. PR (H)" = round(mean(human_professional_referral),2),
                                                        "Overall Average (H)"= round(mean(human_overall_quality),2))
```

# 4. Correlation heatmap
```{r}
# Human (General)
metric_cols <- c("human_accuracy", "human_safety", "human_completeness","human_professional_referral", "human_overall_quality")
corrplot(cor(df_general_annotated[,metric_cols],use="pairwise.complete.obs"), method = "number")

# Human (Specific)
corrplot(cor(df_specific_annotated[,metric_cols],use="pairwise.complete.obs"), method = "number")

# AI (General)
metric_cols <- c("accuracy", "safety", "completeness","professional_referral", "overall_quality")
corrplot(cor(df_general_annotated[,metric_cols],use="pairwise.complete.obs"), method = "number")

# AI (Specific)
corrplot(cor(df_specific_annotated[,metric_cols],use="pairwise.complete.obs"), method = "number")
```

## each model's heatmap

## General
```{r}
# mistral:7b
metric_cols <- c("mistral:7b_accuracy", "mistral:7b_safety", "mistral:7b_completeness","mistral:7b_professional_referral", "mistral:7b_overall_quality")
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number")

# llama3.1:8b
metric_cols <- c("llama3.1:8b_accuracy", "llama3.1:8b_safety", "llama3.1:8b_completeness","llama3.1:8b_professional_referral", "llama3.1:8b_overall_quality")
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number")

# gpt-5.4-mini
metric_cols <- c("gpt-5.4-mini_accuracy", "gpt-5.4-mini_safety", "gpt-5.4-mini_completeness","gpt-5.4-mini_professional_referral", "gpt-5.4-mini_overall_quality")
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number")

# qwen3-vl-32b-instruct
metric_cols <- c("qwen3-vl-32b-instruct_accuracy", "qwen3-vl-32b-instruct_safety", "qwen3-vl-32b-instruct_completeness","qwen3-vl-32b-instruct_professional_referral", "qwen3-vl-32b-instruct_overall_quality")
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)
```

## Specific
```{r}
# mistral:7b
metric_cols <- c("mistral:7b_accuracy", "mistral:7b_safety", "mistral:7b_completeness","mistral:7b_professional_referral", "mistral:7b_overall_quality")
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number")

# llama3.1:8b
metric_cols <- c("llama3.1:8b_accuracy", "llama3.1:8b_safety", "llama3.1:8b_completeness","llama3.1:8b_professional_referral", "llama3.1:8b_overall_quality")
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number")

# gpt-5.4-mini
metric_cols <- c("gpt-5.4-mini_accuracy", "gpt-5.4-mini_safety", "gpt-5.4-mini_completeness","gpt-5.4-mini_professional_referral", "gpt-5.4-mini_overall_quality")
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number")

# qwen3-vl-32b-instruct
metric_cols <- c("qwen3-vl-32b-instruct_accuracy", "qwen3-vl-32b-instruct_safety", "qwen3-vl-32b-instruct_completeness","qwen3-vl-32b-instruct_professional_referral", "qwen3-vl-32b-instruct_overall_quality")
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)
```
## overall
```{r}
# general
metric_cols <- names(df_general)[sapply(df_general, is.numeric)]
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "circle", tl.pos = "n")

# specific
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "circle", tl.pos = "n")
```
## By Metric

```{r}
# general
# Accuracy
metric_cols <- grep("_accuracy$",names(df_general),value=TRUE)
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)
# Safety
metric_cols <- grep("_safety$",names(df_general),value=TRUE)
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)

# Completeness
metric_cols <- grep("_completeness$",names(df_general),value=TRUE)
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)

# Professional Referral
metric_cols <- grep("_professional_referral$",names(df_general),value=TRUE)
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)

# Overall
metric_cols <- grep("_overall_quality$",names(df_general),value=TRUE)
corrplot(cor(df_general[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)
```

```{r}
#specific
# Accuracy
metric_cols <- grep("_accuracy$",names(df_general),value=TRUE)
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)
# Safety
metric_cols <- grep("_safety$",names(df_general),value=TRUE)
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)

# Completeness
metric_cols <- grep("_completeness$",names(df_general),value=TRUE)
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)

# Professional Referral
metric_cols <- grep("_professional_referral$",names(df_general),value=TRUE)
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)

# Overall
metric_cols <- grep("_overall_quality$",names(df_general),value=TRUE)
corrplot(cor(df_specific[,metric_cols],use="pairwise.complete.obs"), method = "number", tl.srt = 45)
```
# 5. Score Distributions

## By model (No Human)
```{r}
#General
# Accuracy
df_general |> pivot_longer(ends_with("_accuracy")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Safety
df_general |> pivot_longer(ends_with("_safety")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Completeness
df_general |> pivot_longer(ends_with("_completeness")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Professional Referral
df_general |> pivot_longer(ends_with("_professional_referral")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Overall
df_general |> pivot_longer(ends_with("_overall_quality")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
#Specific
# Accuracy
df_specific |> pivot_longer(ends_with("_accuracy")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Safety
df_specific |> pivot_longer(ends_with("_safety")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Completeness
df_specific |> pivot_longer(ends_with("_completeness")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Professional Referral
df_specific |> pivot_longer(ends_with("_professional_referral")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Overall
df_specific |> pivot_longer(ends_with("_overall_quality")) |>
  ggplot(aes(name, value)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
## By model (including human)
```{r}
#General
dat <- df_general_annotated %>%
  pivot_longer(cols = c(
    accuracy, safety, completeness, professional_referral, overall_quality,
    human_accuracy, human_safety, human_completeness, human_professional_referral, human_overall_quality),
    names_to = "metric",
    values_to = "score")|> mutate(
    Model = if_else(str_detect(metric, "^human_"), "human", Model),
    metric = str_remove(metric, "^human_")
    )

ggplot(dat, aes(x = score, fill = Model)) +
  geom_density(alpha = 0.2) +
  facet_wrap(~metric, scales = "free_y") +
  labs(title = "Distribution of Model vs. Human Scores",
  x = "Score Value",
  y = "Density",
  fill = "Evaluator / Model") +
  theme_minimal()
```
```{r}
# Specific
dat_spec <- df_specific_annotated %>%
  pivot_longer(cols = c(
    accuracy, safety, completeness, professional_referral, overall_quality,
    human_accuracy, human_safety, human_completeness, human_professional_referral, human_overall_quality),
    names_to = "metric",
    values_to = "score")|> mutate(
    Model = if_else(str_detect(metric, "^human_"), "human", Model),
    metric = str_remove(metric, "^human_")
    )

ggplot(dat_spec, aes(x = score, fill = Model)) +
  geom_density(alpha = 0.2) +
  facet_wrap(~metric, scales = "free_y") +
  labs(title = "Distribution of Model vs. Human Scores",
  x = "Score Value",
  y = "Density",
  fill = "Evaluator / Model") +
  theme_minimal()
```

## By Category (General Only)
```{r}
ggplot(dat, aes(x = score, fill = Category)) +
  geom_density(alpha = 0.2) +
  facet_wrap(~metric, scales = "free_y") +
  labs(title = "Distribution of Model vs. Human Scores",
  x = "Score Value",
  y = "Density",
  fill = "Category") +
  theme_minimal()
```

## By Scenario (General Only)
```{r}
ggplot(dat, aes(x = score, fill = Scenario)) +
  geom_density(alpha = 0.2) +
  facet_wrap(~metric, scales = "free_y") +
  labs(title = "Distribution of Model vs. Human Scores",
  x = "Score Value",
  y = "Density",
  fill = "Scenario") +
  theme_minimal()
```


## By Company (Specific Only)

```{r}
ggplot(dat_spec, aes(x = score, fill = Company)) +
  geom_density(alpha = 0.2) +
  facet_wrap(~metric, scales = "free_y") +
  labs(title = "Distribution of Model vs. Human Scores",
  x = "Score Value",
  y = "Density",
  fill = "Company") +
  theme_minimal()
```



## 6. Response length and prompt length

```{r}
#General
text <- setdiff(df_general |> select(where(is.character)) |> names(),c("Category", "Scenario"))

avg_len <- df_general |> summarise(across(all_of(text), ~ mean(nchar(.), na.rm = TRUE)))
avg_len

barplot(as.numeric(avg_len), names.arg = text,  main = "Average Character Length", ylab = "Characters", cex.names = 0.5)
```

```{r}
#specific
text <- setdiff(df_specific |> select(where(is.character)) |> names(),c("Company", "Reference"))

avg_len <- df_specific |> summarise(across(all_of(text), ~ mean(nchar(.), na.rm = TRUE)))
avg_len

barplot(as.numeric(avg_len), names.arg = text,  main = "Average Character Length", ylab = "Characters", cex.names = 0.5)
```

# 7. Summary Table 

```{r}
# General
summary_gen <-dat |> group_by(Model, metric) |> summarise(
    Mean = mean(score, na.rm = TRUE),
    .groups = "drop") |>
  select(Model, metric, Mean) |> pivot_wider(
    names_from = Model, values_from = Mean)
summary_gen
```

```{r}
summary_gen <-dat_spec |> group_by(Model, metric) |> summarise(
    Mean = mean(score, na.rm = TRUE),
    .groups = "drop") |>
  select(Model, metric, Mean) |> pivot_wider(
    names_from = Model, values_from = Mean)
summary_gen
```


# 8. Isolate generated answers and analyze them
## Worst (By Model, category, etc)
## Best
## Check the tone for each model and note it here
## find anything odd/weird/unique about a model? describe them here!
## put the parameters we used to in the python notebook like token things 
## what is each model known for?
